Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-27 paper_jasa.tex
cleaned up the data cleaning section

\subsection{Data Screening}

@@

{\bf Screening scenarios:} Amazon Mechanical Turk data often suffers from the problem that some participants are trying to 'game' the system -- in our situation, these are participants who did not put in a best effort to identify the data plot, but just randomly picked a plot to maximize their 'winnings'.  In order to avoid using those results, we are comparing six different screening methods for excluded participants from the data analysis. 
%There are six suggested approach to clean the data. 
They are
\begin{enumerate}
\item {\bf include all participants} and their evaluations
\item exclude all participants' evaluations, who did {\bf not} share their {\bf demographic information} (age, gender education level -- all three pieces of information are either missing or all present).
\item exclude participants' records, if {\bf none of the evaluations}  correctly identified the data plot -- every participant was shown a range of `easy' lineups.
\item include participants' records, if   {\bf at least 20 percent} of the evaluations are {\bf correct}  -- based on ten evaluations per participants, two correct evaluations are significant evidence against a person just guessing
\item include participants' records, if at least {\bf 50\% of all very easy lineups are correct} 
\item use easy lineups as {\bf reference charts}: sample one easy lineup from a person's records. If that lineup is evaluated {\bf correctly}, include all (other) lineups of that person, otherwise exclude all lineup evaluations by this participant.
\end{enumerate}

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets. 
Note that in some of the lines the number of male and female participants does not add up to the total number of participants. This is due to missing demographic information. \hh{Do we need this table or could we make this a visual comparison? For me, there's too many numbers with too many digits.}}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 185 & 122 &  63 & 2121 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 & 156 & 106 &  50 & 1681 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

Table \ref{tbl:summary} shows  the summary results after applying different screening on the data. For our analysis we picked criteria six (6) and present results based on this in the following sections.

>>>>

\subsection{Data Cleaning}

@@

%{\bf Screening scenarios:}
Amazon Mechanical Turk workers are paid for their efforts, not substantial, but on the scale of the minimum wage of the USA. Some workers will try to maximize their earnings for minimum effort, which can affect the results from the data. For example, some workers may simply randomly pick a plot, without actively examining the plots in the lineup. For the purposes of identifying these participants and cleaning the data, each block of 10 lineups that a subject received included several very easy ones. One of these was picked at random as the filtering lineup, and action was taken depending on whether they answered correctly or incorrectly. The data of participants who did not answer correctly was removed. For the subjects, who correctly answered the filtering lineup, all of their data was kept, except for that particular lineup. That is, for each block of 10 lineups, only the data from 9 lineups was used for each subject.

%Amazon Mechanical Turk data suffers from the problem that some participants are trying to 'game' the system, because they are being paid for their efforts, not much by the standards of the US minimum wage, but enough to encourage honest efforts.  in our situation, these are participants who did not put in a best effort to identify the data plot, but just randomly picked a plot to maximize their 'winnings'.  In order to avoid using those results, we are comparing six different screening methods for excluded participants from the data analysis. 
%There are six suggested approach to clean the data. 
%They are
%\begin{enumerate}
%\item {\bf include all participants} and their evaluations
%\item exclude all participants' evaluations, who did {\bf not} share their {\bf demographic information} (age, gender education level -- all three pieces of information are either missing or all present).
%\item exclude participants' records, if {\bf none of the evaluations}  correctly identified the data plot -- every participant was shown a range of `easy' lineups.
%\item include participants' records, if   {\bf at least 20 percent} of the evaluations are {\bf correct}  -- based on ten evaluations per participants, two correct evaluations are significant evidence against a person just guessing
%\item include participants' records, if at least {\bf 50\% of all very easy lineups are correct} 
%\item use easy lineups as {\bf reference charts}: sample one easy lineup from a person's records. If that lineup is evaluated {\bf correctly}, include all (other) lineups of that person, otherwise exclude all lineup evaluations by this participant.
%\end{enumerate}

%\begin{table}[hbtp]
%\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets. 
%Note that in some of the lines the number of male and female participants does not add up to the total number of participants. This is due to missing demographic information. \hh{Do we need this table or could we make this a visual comparison? For me, there's too many numbers with too many digits.}}
%\begin{center}
%\begin{tabular}{rrrrr|rrrr|rrrr}
%  \hline
%Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
% \cline{2-5}  \cline{6-9}   \cline{10-13}
%criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
%  \hline
%1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
%  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
%  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
%  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
%  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 185 & 122 &  63 & 2121 \\ 
%  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 & 156 & 106 &  50 & 1681 \\ 
%   \hline
%\end{tabular}
%\end{center}
%\label{tbl:summary}
%\end{table}

\green{Would it make sense to expand this table now to show number of lineups for different experimental conditions?? Maybe not}
\begin{table}[hbtp]
\caption{Number of subjects, gender and total lineups for all three experimental data sets. Note that in some of the lines the number of male and female participants does not add up to the total number of participants due to missing demographic information. }
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
 & \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\ \cline{2-5}  \cline{6-9}   \cline{10-13}
 & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
   & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 & 156 & 106 &  50 & 1681 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

Table \ref{tbl:summary} tabulates the number of subjects, genders and lineups evaluated after applying the data screening procedure.
